Morphological diversity in tenrecs (Afrosoricida, Tenrecidae): Comparing tenrec skull diversity to their closest relatives

### 2015-01-27 paper/Diversity_MS.tex
Full manuscript draft

%-----------------------------------------
%Title page? NB PeerJ say that they don't need a title page
%----------------------------------------
\title{}

@@

\mstitlepage			% Instead of \maketitle you can use the nice template to get it looking like a manuscript
\parindent=1.5em		% Changes paragraph indenting so it's not so big
\addtolength{\parskip}{.3em} % Changes spacing between sections so it's smaller
%****************************************************

%Abstract in a separate document for PeerJ
%****************************************************
\section{Introduction}

@@

	The methods we used involved several steps of data collection, geometric morphometrics analyses and comparisons of morphological diversity. For clarity,  Figure \ref{fig:flow} summarises all of these steps and we describe them in detail below.  	
%Methods flow chart
	\begin{figure}[!htbp]
	\centering
	\includegraphics[width=1\linewidth,height=0.8\textheight]{figures/methods_flowchart_paper.png}

@@

\subsubsection{Landmark placement on images}

@@

	Figure (REF) depicts that landmarks and curves which we used for each of the sets of photographs. For landmarks which are defined by dental structures, we used published dental sources \citep{Repenning1967, Eisenberg1969, Nowak1983, MacPhee1987, KnoxJones1992, Davis1997, Querouil2001, Nagorsen2002, Wilson2005, Goodman2006, Karatas2007, Hoffmann2008, Asher2008,  Muldoon2009, Lin2010} where available to identify the number and type of teeth in each species. Detailed descriptions of the landmarks can be found in the supplementary material.
%****************************************************
	%Put the landmark tables into supplementary

	%Add the landmarks picture: three skulls together

	%Maybe put morphometrics error checking into the supplementary as well?
%***************************************************

@@

\subsection{Results}
	Figure \ref{fig:threePCA} depicts the morphospaces defined by the first two principal component (PC) axes from our principal components analyses (PCAs) of skull and mandible morphologies. The PCAs are based on the average Procrustes -superimposed shape coordinates for skulls in three views (dorsal, ventral and lateral).
%-----------------------------
%PCA figure with three plots
%PCA figure
	%From the diversity_PCAplots_3panel
	\begin{figure}[!htbp]
	\centering
	\includegraphics[width=1\linewidth, height=1\textheight, keepaspectratio]{figures/PCA_threeplot.png}
	\caption[Morphospace (principal components) plot of morphological diversity in tenrec and golden mole skulls.]
		{Principal components plots of the morphospaces occupied by tenrecs (triangles, n=31 species) and golden moles (circles, n=12 species) for the skulls in dorsal (top left), ventral (top right) and lateral (bottom left) views. Each point represents the average skull shape of an individual species. Axes are principal component 1 (PC1) and principal component 2 (PC2) of the average scores from principal components analyses of mean Procrustes shape coordinates for each species.}
	\label{fig:threePCA}
	\end{figure}
%--------------------------
	To compare morphological diversity in the two families, we used the PC axes which accounted for 95\% of the cumulative variation in each of the skull analyses: dorsal (n=6 axes), ventral (n=7 axes) and lateral (n=7 axes). First, we compared the position of each Family within the morphospace plots. Tenrecs and golden moles occupy significantly different positions in the dorsal (npMANOVA: F\textsubscript{1,42}=68.13, R$^2$=0.62, p=0.001 ), ventral (npMANOVA: F\textsubscript{1,42}=103.33, R$^2$=0.72 , p=0.001 ) and lateral (npMANOVA: F\textsubscript{1,42}=76.7, R$^2$ =0.65, p=0.001 ) skull morphospaces,  indicating that the Families have very different, non-overlapping cranial and mandible morphologies (Figure \ref{threePCA}.

>>>>

%-----------------------------------------
%Current title page 
%NB PeerJ don't want a title page: just the author details but I haven't figured out how to do that without losing the formatting of the rest of the manuscript
%I may need to get rid of the lists of tables and figures at the end: they want titles and legends to be on the same page as the figure/table
%----------------------------------------
\title{Morphological diversity in tenrecs (Afrosoricida, Tenrecidae): Comparing tenrec skull diversity to their closest relatives}

@@

\mstitlepage			% Instead of \maketitle you can use the nice template to get it looking like a manuscript
\parindent=1.5em		% Changes paragraph indenting so it's not so big
\addtolength{\parskip}{.3em} % Changes spacing between sections so it's smaller
%****************************************************
%Abstract
%Peer J wants the abstract as a separate document

%****************************************************
\section{Introduction}

@@

	The methods we used involved several steps of data collection, geometric morphometrics analyses and comparisons of morphological diversity. These included i) data collection, ii)geometric morphometric analyses and iii)estimating morphological diversity. For clarity,  Figure \ref{fig:flow} summarises all of these steps and we describe them in detail below.

%Methods flow chart
	\begin{figure}[!htbp]
	\centering
	\includegraphics[width=1\linewidth,height=0.8\textheight]{figures/methods_flowchart_paper.png}

@@

@@

	Figure \ref{fig:landmarks} depicts that landmarks and curves which we used for each of the sets of photographs. For landmarks which are defined by dental structures, we used published dental sources \citep{Repenning1967, Eisenberg1969, Nowak1983, MacPhee1987, KnoxJones1992, Davis1997, Querouil2001, Nagorsen2002, Wilson2005, Goodman2006, Karatas2007, Hoffmann2008, Asher2008,  Muldoon2009, Lin2010} where available to identify the number and type of teeth in each species. Detailed descriptions of the landmarks can be found in the supplementary material.
%****************************************************	
	%Landmark pictures: 3 skulls together	
	\begin{figure}[!htbp]
		\centering
		\includegraphics[width=1\linewidth]{figures/skdors+skvent+sklat_BW.png}
		\caption[Skulls: dorsal, ventral and lateral landmarks]
		{Landmarks (numbered points) and curves (outlines) for the skulls in dorsal,ventral and lateral view. See the supplementary material for detailed landmark descriptions. The skulls are two different specimens of \textit{Potamogale velox} (otter shrew tenrec), museum accession numbers AMNH 51327 (dorsal picture) and BMNH 1934.6.16.2 (ventral and lateral pictures). }
		\label{fig:landmarks}
	\end{figure}

	%Maybe put morphometrics error checking into the supplementary as well?
	%Put the landmark tables into supplementary
%***************************************************

@@

\subsection{Results}
	Figure \ref{fig:threePCA} depicts the morphospaces defined by the first two principal component (PC) axes from our principal components analyses (PCAs) of skull and mandible morphologies. The PCAs are based on the average Procrustes -superimposed shape coordinates for skulls in three views (dorsal, ventral and lateral).
%-----------------------------
%PCA figure with three plots
%PCA figure
	%From the diversity_PCAplots_3panel
	\begin{figure}[!htbp]
	\centering
	\includegraphics[width=1\linewidth, height=1\textheight, keepaspectratio]{figures/PCA_threeplot.png}
	\caption[Morphospace (principal components) plot of morphological diversity in tenrec and golden mole skulls.]
		{Principal components plots of the morphospaces occupied by tenrecs (triangles, n=31 species) and golden moles (circles, n=12 species) for the skulls in dorsal (top left), ventral (top right) and lateral (bottom left) views. Each point represents the average skull shape of an individual species. Axes are principal component 1 (PC1) and principal component 2 (PC2) of the average scores from principal components analyses of mean Procrustes shape coordinates for each species.}
	\label{fig:threePCA}
	\end{figure}
%--------------------------
	To compare morphological diversity in the two families, we used the PC axes which accounted for 95\% of the cumulative variation in each of the skull analyses: dorsal (n=6 axes), ventral (n=7 axes) and lateral (n=7 axes). First, we compared the position of each Family within the morphospace plots. Tenrecs and golden moles occupy significantly different positions in the dorsal (npMANOVA: F\textsubscript{1,42}=68.13, R$^2$=0.62, p=0.001 ), ventral (npMANOVA: F\textsubscript{1,42}=103.33, R$^2$=0.72 , p=0.001 ) and lateral (npMANOVA: F\textsubscript{1,42}=76.7, R$^2$ =0.65, p=0.001 ) skull morphospaces,  indicating that the Families have very different, non-overlapping cranial and mandible morphologies (Figure \ref{fig:threePCA}.
